\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-08 poster/main.tex
update poster Objectives

\begin{block}{Objectives}
\begin{columns} % Subdivide the first main column
\begin{column}{.65\textwidth}
\noindent Design a differentially private Bayesian inference mechanism by scaling to a metric between distribution.
\begin{enumerate}
\item A differentially private Bayesian mechanism,
\item Calibrating mechanism noise by the same probabilistic metric we want to measure accuracy with.
\item Applying smooth sensitivity in mechanism to achieve better accuracy. This is motivated by the Fig. \ref{fig_sensitivity} that local sensitivity is very steep in edge but very smooth in center part.
\end{enumerate}
\end{column}
\begin{column}{.3\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{poster_0.eps}
\caption{Hellinger Sensitivity}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Differentially private Bayesian inference}
Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.

@@

\begin{block}{Smoothed Hellinger Distance based Exponential Mechanism}

>>>>

\begin{block}{Objectives}
\begin{columns} % Subdivide the first main column
\begin{column}{.62\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Calibrating mechanism noise by the same probabilistic metric we want to measure accuracy with.
\item Applying smooth sensitivity in mechanism to achieve better accuracy. This is motivated by Fig. \ref{fig_sensitivity} that local sensitivity is very steep in edge but very smooth in center part.
\end{enumerate}
\end{column}
\begin{column}{.35\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.85\textwidth]{poster_0.eps}
\caption{Hellinger Sensitivity}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Differentially Private Bayesian inference}
Release a private version of posterior distribution $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.

@@

\begin{block}{Smoothed Hellinger Distance Based Exponential Mechanism}
